The letter

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
final, final edit before removing the cross-referncing

In this study, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel. In future work, we plan to relax this assumption. In addition, we have assumed that the neural field is isotropic and homogeneous. It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic. However, the assumption of homogeneity is quite strong as the size of the neural field becomes larger. Future work should focus on developing estimation algorithms where assumptions of homogeneity can be relaxed. Future work should also include a synaptic response kernel with finite rise and decay times, and a finite distant-dependant action potential propagation velocity into the parametric neural field equations.

% Do NOT remove this, even if you are not including acknowledgments
\section*{Acknowledgments}
Dean Freestone would like to thank Dr. Mark van Rossum for hosting him while visiting the University of Edinburgh where this work was undertaken and Matt. Parham Aram would also like to thank Andrew Hills for useful discussions and assistance with code and the generation of figures.

>>>>

In this study, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel. In future work, we plan to relax this assumption. In addition, we have assumed that the neural field is isotropic and homogeneous. It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic. However, the assumption of homogeneity is quite strong as the size of the neural field becomes larger. Future work should focus on developing estimation algorithms where assumptions of homogeneity can be relaxed. In addition, natural extensions of this framework are the inclusion of a post-synaptic response kernel with a finite rise and decay time, and a finite distant-dependant action potential propagation velocity into the parametric neural field equations.

% Do NOT remove this, even if you are not including acknowledgments
\section*{Acknowledgments}
Dean Freestone would like to thank Dr. Mark van Rossum for hosting him while visiting the University of Edinburgh where this work was undertaken and Dr. Matthias Hennig for useful discussions and feedback. Parham Aram would also like to thank Andrew Hills for useful discussions and assistance with code and the generation of figures.
